---
title: "638_A1"
author: "Zhenlian"
date: "Jul 14, 2017"
output:
  html_document: default
  pdf_document: default
---
```{r}
#libaries
library(readr)
library(ggplot2)

library(dplyr)
library(gridExtra)
library(grid)



```

```{r}
#import csv file.
WD<-getwd()
if(!is.null(WD)) setwd(WD)
raw = read.csv('../data/data_PHMX638_A1.csv', header = TRUE)[-1,]




```
```{r}
#Check data structure, change to numeric columns accordingly.  

cols <- c("TIME", "DV", "AMT")

for (col in cols){
  
 raw[[col]]<- as.numeric(as.character(raw[[col]]))
}

str(raw)
```





```{r}
#histogram of age and weight:
demo<-raw%>%filter(!duplicated(id))%>%select(id,WT,AGE,RACEN, GENDER)


weight<-ggplot(demo, aes(x=WT)) +
  #geom_histogram() + 
  geom_histogram(binwidth=5,color="blue",fill="white")+
  ggtitle("Weight distribution")+
  xlab("Weight(kg)") +
  ylab("Count")
AGE<-ggplot(demo, aes(x=AGE)) +
  #geom_histogram() + 
  geom_histogram(binwidth=5,color="red",fill="white")+
  ggtitle("AGE distribution")+
  xlab("Age (years)") +
  ylab("Count")

#Gender and race distribution:
gender<-demo%>%count(GENDER)%>%mutate(freq=n/sum(n))
gender
race<-demo%>%count(RACEN)%>%mutate(freq=n/sum(n))
race


#arrange weight, Age in one panel

grid.arrange(weight,AGE,ncol=2)


```
#If needed, Histogram of gender and race distribution:
demo$GENDER<-as.factor(demo$GENDER)   ##need to change to factor otherwise the legend won't shown after customized.
str(demo)
gender_his<-ggplot(demo, aes(GENDER))+
  geom_bar() +
  ylab("Count")+
  labs(title="Gender distribution")+
  scale_x_discrete(name="Gender",labels=c("0"="Female","1"="Male"))
 
 
   
race_his<-ggplot(demo, aes(RACEN))+
  geom_bar()+
  labs(title="Race distribution",x="Race Codes",y="Count")


```{r}
#Check correlation of demographic variables:
demo<-demo%>%select(AGE,WT,RACEN,GENDER)

cor(demo)
```



```{r}
#Use facet.grid to plot both DG100 and DG250:

#First change the two "levels" in DOSE to 100 mg and 250 mg. 
levels(raw$DOSE)<-c("100mg","250mg")  #can be only one level?
raw$DOSE<-as.factor(as.character(raw$DOSE))
P1<-ggplot(raw, aes(x=TIME, y=DV,group_by(id),color=factor(FORMULATION))) + 
geom_point() +
  aes(color=factor(FORMULATION,labels=c("0"="IV","1"="ORAL")))+stat_summary(fun.y=mean,geom="line",size=2)+
  facet_grid(.~DOSE)+
  theme(legend.title=element_blank())+
  ylab("Concentration(ug/L)")+
  xlab("TIME(hr)")
P1
P2<-P1+scale_y_log10()
P2

```

